AddMore
\begin{itemize}
	\item Can you please add 5 more?
	\item I want to add 3 more.
	\item Will you please add 4 more?
	\item Let's add 2 more.
	\item Add 8 more.
	\item I need 3 more.
\end{itemize}

ClearBasket
\begin{itemize}
	\item I want to clear my basket.
	\item Can you remove my basket?
	\item I want my basket to be empty.
	\item Can you delete everything from my basket?
	\item Clear my basket.
	\item Empty my shopping list.
\end{itemize}

DeleteItem
\begin{itemize}
	\item Can you remove this from my shopping list?
	\item I want to remove this item.
	\item Please, delete this from my shopping list.
	\item Will you remove this from my basket?
	\item Delete item.
	\item Remove this.
\end{itemize}

FindItem
\begin{itemize}
	\item I want to add some salami.
	\item Can you find salami for me please?
	\item I would like to find 5 beers.
	\item I want to find some beers.
	\item I need 8 more beers please.
	\item I am looking for catfood.
\end{itemize}

Greeting
\begin{itemize}
	\item Hi, my name is Ivor.
	\item Good morning, I'm Ivor.
	\item Hello, how are you?
	\item Good evening.
	\item Hello, what's up?
	\item Hello.
\end{itemize}

Help
\begin{itemize}
	\item Please, I need help.
	\item Can you help me with this?
	\item What is this?
	\item I don't get it how this works.
	\item I want help.
	\item Please, help me.
\end{itemize}

RemoveMore
\begin{itemize}
	\item Can you remove these items?
	\item I want to remove this 2 times.
	\item Can you please remove this a couple of times?
	\item Remove 5 pieces from this item.
	\item Remove 8 items.
	\item Remove items.
\end{itemize}

ShowBasket
\begin{itemize}
	\item I want to see my basket.
	\item Can you show me my shopping list?
	\item What's in my cart?
	\item Please, show my cart.
	\item Show my shopping basket?
	\item Please, show me my basket.
\end{itemize}

ShowProfile
\begin{itemize}
	\item I want to see my profile.
	\item Can you show me my information?
	\item What's my profile information?
	\item Show my profile.
	\item What's my name.
	\item Show my username.
\end{itemize}

Stop
\begin{itemize}
	\item Can you stop?
	\item Please start over again.
	\item I want to exit.
	\item Let's quit.
	\item Can I stop?
	\item Make it stop.
\end{itemize}

UpdateProfile
\begin{itemize}
	\item I want to update my name.
	\item Can you change my username?
	\item Update my profile please.
	\item Will you change my username?
	\item Change my name.
	\item Update my username.
\end{itemize}